DRAFT: Harmonized and trait aggregation paper

### 2020-12-03 Paper/Draft_harmonization_paper.tex
03.12.2020: Update Discussion

To our knowledge, only Brown et al. \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates. We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents. To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}. In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology. However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, schneider_towards_2019}. Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.

Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty how the trait is expressed in any particular organism (e.g. adult terrestrial stage, presence of gills) or continuous (e.g. tolerance of pollution, body size). One approach for dealing with uncertainty is the use of fuzzy coded grouping features, where the traits are assigned probabilistic values. Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions. In this study we denote the proportionate description (0-1) of traits as affinities or affinity scores.

@@

Various codings of traits are used throughout the databases (e.g. binary, fuzzy, continuous). The freshwaterecology.info and Australian use different codings in their databases. Tachet and the New Zealand database exclusively use fuzzy coding. Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).

@@

\subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}

Our results indicated that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level. However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean. The different weightings used by the aggregation methods, i.e. aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets. This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}. Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits. A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have low numbers of genera or species entries. From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level. 52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}). In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level. 67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}). The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family. % How often in the trait datasets?

% Improve wording
Observed differences between aggregated and assigned traits were higher for the North American trait dataset. This can be explained by the binary coding of the traits in the North American dataset. As a result, traits have been assigned affinities of either 1 or 0.  Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.

% Discussion on differences between aggregated and assigned traits  
Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing. Some traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
% ?Mention intra-species variation of some traits (voltinism varies along climatic gradients)
% ? Mention: obtaining trait information on species-level is challenging
% Could lead to data gaps in the datasets
% ?Would like to connect both parts, but maybe this doesn't make too much sense
Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits. The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits. Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32). % A reason for this is also that body size was coded binary.
For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1). Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3). % So these traits might be highly variable, confirming the earlier mentioned studies partially.

% Conclude:
% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
% Fuzzy coding is one option to express uncertainty but is not only used for variabality in traits within taxononomic groups above species-level. Also, for variation in traits during development of an organism,
% ? 
% ? Other measures possible, e.g. report SD

% Include?:
% Which traits are more consistent
% How have the aggregation and assignments performed when looking back at the original data?
% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
%   - Where does the classification come from?
%     Few sources used in NOA also used in AUS:
%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used for feeding mode
%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?

The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study. The traits that did not respond t<o the salinity gradient (i.e. not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits. During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder). As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}). Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.

% Situation with Resp gil complicated: 
% - Original data has a lot of zeros, which are not anymore present in the harmonized & aggregated datasets (see Table S2)
% - In the analysis with the harmonized dataset resp_gil is not responding to the salinity gradient 
% - Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
% responding to conductivity!

% Why did some aggregated datasets promote life cycle duration traits and others not?
% - Results using trait data obtained when aggregating with stepwise_agg (median) and stepwise_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites. 
% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites.
% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets.

% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions. I wonder if this indicates that Family richness is really higher in Australia. Perhaps it might be as Australia has a wider range of evolutionary histories. This would be worth considering in the discussion

>>>>

To our knowledge, only Brown et al. \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates. We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents. To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}. In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology. However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, kissling_towards_2018}. Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.

Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty how the trait is expressed in any particular organism (e.g. adult terrestrial stage, presence of gills) or continuous (e.g. tolerance of pollution, body size). One approach for dealing with uncertainty is the use of fuzzy coding, where the traits are assigned probabilistic values. Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions. In this study we denote the probabilistic values (0-1) of traits as affinities or affinity scores.

@@

Various codings to describe traits are used throughout the databases (e.g. binary, fuzzy, continuous). The freshwaterecology.info and Australian use different codings in their databases. Tachet and the New Zealand database exclusively use fuzzy coding. Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).

@@

% 1. Allgemeiner Satz zum Thema, der auf eine offene Frage o.ä. hinweist
% 2. Was haben wir herausgefunden?
% 3. Was haben andere schon herausgefunden
% 4. Was bedeutet das für zukünftige Studien?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. Trait Database 
%- Unterschiede zwischen Regionen und Trait Genauigkeit
%- Was kann man machen
%- Andere Studien zur Trait Harmonisierung usw.

% Why do we need trait-based analysis, especially across regions?
Synthesizing trait information from various trait databases is crucial to unfold the full potential of trait-based approaches, e.g. for studying community trait responses to environmental gradients worldwide. Our attempt of harmonising trait information from multiple trait databases showed that grouping feature harmonisation is labour-intensive because grouping features are differentiated differently into traits between trait databases. In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to amalgamate these traits (e.g. the trait piercer in the Tachet database, Table \ref{tab:traits_harmonization}). Thus, the field of freshwater ecology needs terminological standards to facilitate data synthesis. Harmonised definitions and concepts of traits have been for example developed for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}. The core of this harmonisation initiative is not only to provide standardized trait definitions but also to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field. Such initiatives could be a role model for freshwater science to establish unambiguous terminologies for invertebrate traits. The existing freshwater invertebrate trait databases could then be linked through standardised terminologies or ontologies, as suggested by Baird et al. almost a decade ago \cite{baird_toward_2011}. By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies \cite{schneider_towards_2019}. Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately improve interpretation of derived results. % What is not mentioned here is how traits are measured, for which measurement protocols exist I believe. I think this is an separate issue.

%%% No section on codings?
% Besides semantic heterogeneity between traits and grouping features, codings used to describe traits differ between trait databases. % We showed that fuzzy coded and binary coded could be used together but a lot of assumptions have been made here?
%%% Section to different codings -> what is an appropriate question?
% Maybe this section is not necessary and just one or two sentences to various codings is sufficient
% The European and Australian trait databases use several codings for their traits (fuzzy, binary and continuous) while the North American databases only use binary coding and the New Zealand database only fuzzy coding. % due to a lack of species trait information.
% Differences in fuzzy coding:
% freshecol: 
% It is based on the average distributions, occurrences or behaviours of a taxon within the environmental gradient or organismic flexibility under consideration. The ten point assignment system was first introduced by Zelinka and Marvan (1961) for the classification of saprobic valences and was extended by Moog (1995) to other parameters, such as stream zonation preferences and feeding types. Within freshwaterecology.info the ten point assignment system was used for coding the majority of those parameters, which comprise several categories.
% Example for the parameter "stream zonation preference": If 70% of a species’ records are observed in spring brooks and 30% in the upper trout region, 7 out of 10 points will be allocated to the category "hypocrenal" (spring brook) and 3 points to "epirhithral" (upper trout region) to describe the expected occurrence of this species within the longitudinal zonation of a river. For all other categories "0" will be used.
% Tachet: 0 - 5: Thereby, the relevant features of a taxon were described by the relative distribution of the information among the categories of each trait. This procedure was a pertinent and simple way to "translate" the available knowledge about species traits of organisms into numerical values. It also avoided the obligate assignment of a taxon to a single category, which can lead to inaccurate characterisation of biological or ecological trait profiles
% Can be converted so that they can be used together 
% As already stated fuzzy coding is used to express uncertainty in traits, for variability in traits within taxononomic groups above species-level or for variation in traits during the development of an organism. So it's not really clear for fuzzy coded taxa on family-level what uncertainty is expressed
% Fuzzy coding captures uncertainty. Nice way but has also drawbacks -> correlated variables, needs specific statistic methods, cannot be used in bayesian priors etc.
% Binary coding is, transformed to 0 and 1, and thus converted just a "variant" of fuzzy coding?
% Problems fuzzy coding: Which uncertainty do they cover?
% Stay focused! Schneide nicht zu viele Themen an - Du musst nicht jedes einzelne Thema diskutieren. Generell kann die Diskussion so 3-4 Abschnitte haben, die jeweils die wichtigsten Resultate oder Aspekte diskutieren. Eine generelle Diskussion der Fuzzy Coding und intra-species variation wäre aus meiner Sicht eher ein eigener, wenn auch nicht allzulanger Abschnit
% \textit{\color{blue} Ideas for concluding this section:
% \begin{itemize}
%   \item The uncertainty of trait information should be taken into account when aggregating traits and appropriate measures to capture this uncertainty should be established.
%   \item Are other measures of uncertainty thinkable, e.g. based on SD or Variance 
% \end{itemize}
% }

%%%%%%% Section on taxonomic levels and data coverage
%? What's the problem with the state of data coverage
Our analysis aimed to use most of the available trait information for different regions to establish harmonised grouping feature datasets. Although many taxa are coverd in the trait databases, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
% freshwaterecolgy.info on species-level, Australia mainy taxa on genus and family-level
% Pointing to the problem of how accurate information on levels with lower taxonomic precision is 
% For some groups, species and genus-level identification important since information varies considerably in these groups; see Serra Paper!
% Erwähnen? Obtaining trait information on species-level is challenging
% How would this change our results?

% Include Ben's point?
% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions. I wonder if this indicates that Family richness is really higher in Australia. Perhaps it might be as Australia has a wider range of evolutionary histories. This would be worth considering in the discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. + 3. die aktuellen Abschnitte (obwohl sie auch etwas ähnliche Themen beinhalten - geht ja immer um was ähnliches - wie gut sind die Aggregationsmethoden - könnte man vielleicht auch zusammenfassen
% Hier: Überschrift mit genereller Aussage?

% Why is it important to investigate trait aggregation methods? And trait harmonisation?

% R: Man könnte das ggf. auch an den Anfang ziehen. Also einleitend: Warum ist die Frage wichtig, was haben wir überhaupt gemacht - und dann eben erst mal sagen, dass die Analysen zwischen aggregated und assigned traits jetzt nicht die ultimative Wahrheit sind. Gleichwohl unsere Ergebnisse anzeigen können, welche Methoden überhaupt und unter welchen Umständen zu unterschiedlichen Ergebnissen führen, so dass die Leser dort entsprechend vorsichtig sein müssten

As outlined in the introduction, various trait aggregation methods are used by researchers when trait data are on more precise taxonomic levels than observational data. We aggregated traits from an Australian and North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions. Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing. Some traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}. However, if trait aggregation is necessary our study can give guidance, under which circumstances the choice of aggregation method might be important. The 5 aggregation methods we tested use either the mean or the median and different weightings. Our results indicated that 1) aggregation of traits using \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{mean}} (median aggregation methods) compared to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_mean} (mean aggregation methods) is often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities. We obtained for both datasets more differing cases for mean aggregation methods, irrespective of the weighting. In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases). In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}). However, when there were differences between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American trait dataset. The mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}). The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits for North America. As a result, traits have affinities of either 1 or 0. Therefore, traits of a particular grouping feature have in most cases a higher difference in trait affinities to each other than if they were fuzzy coded. Using the median to aggregate binary coded taxa will often result in a value of 0 or 1, while using the mean will often result in values between 0 and 1. Thus, using the median led for the North American dataset in many cases either to agreement with the assigned traits or the difference between median aggregated traits and assigned traits was often 1. 
% except for traits were binary coding was not mutually exclusive and when same number of 0 and 1
% Binary coding also explains the amount of differing cases, median often right for binary data, must be cautious when a lot of traits are unknown?
The number of differing cases and the mean absolute differences to the assigned traits were similar within the mean aggregation and within the median aggregation methods, which confirms our second finding, the small influence of weighting on the aggregation methods. Furthermore, the distributions of absolute trait affinity differences to assigned traits obtained were relatively similar for the mean aggregation methods and the median aggregation methods in both tested datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}). The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries. From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 14 \% were resolved on family-level and 62 \% were resolved on genus-level. 52 \% had 5 or less genera and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}). In the Australian dataset 21 \% of the taxa were resolved on family-level, 40 \% were resolved on genus level, and 39 \% were resolved on species-level. 68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).

Although the simulation results showed only small differences between the results of the aggregation methods the choice of the aggregation method for small numbers of genera per family can be important when one genus has a much larger number of species compared to other genera within a particular family. 
% R: Das Argument ist schwer greifbar für den Leser - es wäre einfacher zu folgen, wenn Du schreiben würdest, wann man denn mit unterschieden rechnen würde und warum - und dann deine Daten beschreiben. Also wenn es sehr viele Genera und diese mit sehr unterschiedlicher Anzahl an Arten wären usw. . Die Diskussion sollte vor allen Dingen allgemeiner verständniclih sein und nicht technisch die Resultate fortsetzen.

% R: Allgemein in Trait data sets - ja geht in die Richtung, wobei du ja hier nicht noch analysen für alle möglichen Tiere und traits machen kannst, aber zumindest aufzeigen unter welchen Umständen es bedeutsam ist - und was dann gemacht werden sollte. Der Leser will ja aus der Diskussion etwas mitnehmen, ggf. auch was er tun soll
\textit{\color{blue} Maybe include: How often does such a taxonomic data occur in the trait datasets?}
% Das liest sich wie einer erweiterte Resultate Sectioin - das ist nicht Sinn der Diskussion. Du sollst da nicht neue Ergebnisse vorstellen sondern dann eher auf eine Abbildung verweisen und in der Regel in 2-3 Sätzen die Ergebnissen in einfachen Sätzen nennen und diskutieren d.h. in Kontext anderer Studien stellen - oder wenn es diese nicht gibt, was auch gesagt werden müsste, dann sagen, was daraus folgt.

% R: Misses a starting sentence, Why did we conduct this analysis?
In the re-analysis where we investigated how using harmonised and aggregated traits might change the results of trait-environment relationships we found similar results compared the original study. Traits that responded only in the original analysis but were non-response in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits. For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder). As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}). Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.

% Keep it simple!
% Resp gills: Original data has a lot of zeros, which are not present in the harmonized \& aggregated datasets (see % In the analysis with the harmonized dataset resp gills is not responding to the salinity gradient
% Aggregated data look similar to the harmonized ones, but resp gills is here one of the traits responding to conductivity!
% Why did some aggregated datasets promote life cycle duration traits and others not
% Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Ausblick und offene Fragen für zukünftige Studien

% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
% quality evaluation of traits als Thema..

% Where does the classification come from? Few sources used in NOA also used in AUS:
% AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
% NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used for feeding mode
